%-------------------------
% Resume in Latex
% Author : Nader Rais
% Website: https://github.com/nerosiar/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://nrais.me/}{\Large Nader RAIS (Security Engineering Student)}} & Email : \href{mailto:nader.hajboubakerrais@esprit.tn}{nader.hajboubakerrais@esprit.tn}\\
  \href{http://nrais.me/}{http://www.nrais.me} & Mobile : +216-21585236 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ESPRIT Hight Private School of Engeneering and Technologies}{Ariana, Tunisia}
      {Bachelor of Engineering in Computer Science (field of network infrastructure and data security)}{Sep. 2018 -- Jun. 2021}
    \resumeSubheading
      {Sfax Preparatory School}{Sfax, Tunisia}
      {Preparatory Degree Mathematics and Physics}{Sept. 2015 -- July. 2018}
    \resumeSubheading
      {Djerba Lycée Technique}{Djerba, Tunisia}
      {Bachelor of Maths}{June. 2015 }
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Freelance ; SelfEmployed}{Tunis, Tunisia}
      {Software Engineer}      {Jan 2018 - Oct 2020}
      \resumeItemListStart
        \resumeItem{Netflow Filtration }
          {Network packet recommender systems using collaborative filtering on ntopng datasets using Tensorflow, python ASGI uvicorn, FastAPI, Mysql SQLAlchemy and Angular.}
        \resumeItem{Service Management }
          {Managing sailsjs microservices on AWS instances using Load Balancer and Cluster automation such as delivery time optimization, tracking, queuing and A/B testing.}
        \resumeItem{Bulk Order}
          {Bulk data processing and injection service from Hadoop to Cassandra and provides a REST layer .}
        \resumeItem{Workflows}
          {Built an internal app to run threat intelligence hunting by Servers monitoring for streaming data-parallel processing pipelines.Also creating a strategy backtesting engine used for simulating threats.}
        \resumeItem{System Tracking and Data Collection}
          {Designed the survey sourcing platform for an exportation Company which allowed for creating various tasks for exportations embedding surveys.}
        \resumeItem{Warehousing}
          {Setup, schema design and management of Amazon Redshift. Built an internal app for access to the data using a web interface. Dataduct integration for daily ETL(Extract, transform, load) injection into Redshift.}
        \resumeItemListEnd

    \resumeSubheading
      {IOWAVES}{Monplaisir Ariana , Tunisia}
      {Junior Developer}{Jul.2019 -- Sept.2019}
      \resumeItemListStart
        \resumeItem{iovision}
          {Developed Monitoring dashboards and data surveying tools, which helped Energy  Engineers run their calculations better by providing data in real-time (NodeJS, socketio, Angular , Mongodb).}
        \resumeItem{IoTrant}
          {Created an IoT based network with Xbees and raspberry PI 3B for collecting data from electrical machines using zigbee transfert protocol and MQTT.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Consommi Tounsi}
      {Ecommerce platform for Tunisian products, To enhance the financial envirenment. JEE, Wildfly.}
    \resumeSubItem{educloud SOC Visualization}
      {Data Visualization of educloud network Logs data using D3 and MongoDB.}
    \resumeSubItem{MyGym}
      {Development of a Desktop application for a Gym hall with C and Glade.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Prog Languages}{: Python, Scala, Javascript, JAVA, Rust, C}
     \hfill
     \textbf{Technologies}{: Nodejs, VueJS, JEE/spring}
    }
    \item{
     \textbf{Cloud}{: AWS, Openstack, Docker, kubernetes, Jenkins, Ansible, Kafka}
     \hfill
     \textbf{Monitoring}{: Splunk, ELK, Zabbix}
    }
    \item{ 
     \textbf{Security}{: Metasploit, Forensics, Pwn, Snort, IDS/IPS, Firewalling}
     \hfill
     \textbf{Versioning}{: Git, Bitbucket}
   }
   \item{
     \textbf{Experience In Linux commands and Scripts}{ daily user }
     \textbf{Virtual Envirenment}{: KVM, VMware, Vbox}
    }
 \resumeSubHeadingListEnd

%-----------Languages-----------------
\section{Languages}
  \resumeSubHeadingListStart
    \item{
     \textbf{English}{: B2 professional level, read write and spoken}
     \hfill
     \textbf{Frensh}{: B2 professional level, Fluent}
    }
    \item{
     \textbf{Arabic}{: Native Language}
     \hfill
     \textbf{Spanish}{: Medium Level read and spoken}
    }
  \resumeSubHeadingListEnd
  
%-----------Hibbies & SoftSkills-----------------
\section{SoftSkills And Hobbies}
  \resumeSubHeadingListStart
\item{
     \textbf{Chess Playing}{: Organize and play chess tournaments}
     \hfill
     \textbf{codingamer}{: day to day player at codingame.com}
    }
    \item{
     \textbf{Camping}{: Head of a camping group}
     \textbf{Golf}{: Member of Djerba Regional Team}
     \textbf{CTF player}{: Staff on vulnhub}
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}